Handbook streamFind: Backend

### 2023-09-07 README.Rmd
Updated StreamFindData calls and pkgdown

The supplementary [streamFindData](https://github.com/odea-project/streamFindData) R package holds the data used in examples and other documentation assets of the StreamFind R package and can also be installed from the GitHub repository.

```{r install-streamfinddata, eval=FALSE}
remotes::install_github("odea-project/streamFindData")
```

>>>>

The supplementary [StreamFindData](https://github.com/odea-project/StreamFindData) R package holds the data used in examples and other documentation assets of the StreamFind R package and can also be installed from the GitHub repository.

```{r install-streamfinddata, eval=FALSE}
remotes::install_github("odea-project/StreamFindData")
```
